---
title: "Markdown"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eruptions, echo=FALSE}

```

## Homework 14 part 1

LP Brewery is coming up with a hot new brew called `The Barrel-Aged Dantzig`. Because it is a special craft beer, it has a margin of $30, It uses 10 pounds of `corn`, 4 oz of `hops` and 15 pounds of `malt`. With the addition of this new brew, LP Brewery has to now think about allocating its personnel to the different manufacturing processes. Each of the kegs takes 5 (Hopatronic), 10 (All American), and 20 (Dantzig) hours of labor to make and we have only 5 employees full-time. If this is the production planning for a month of brewing, what is the optimal amount of each beer that must be produced to maximize profit
```{r warning=FALSE,echo=FALSE,message=FALSE}
library(lpSolve)
f.obj <- c(13,23,30)

f.con <- matrix(c(5,15,10,  #corn
                  4,4,4,    #hops
                  35,20,15, #malt
                  5,10,20), #hours of labor
                nrow = 4, byrow = TRUE)

f.dir <- c("<=",
           "<=",
           "<=",
           "<=")

f.rhs <- c(480, #total corn
           160,  #total hops
           1190, #total malt
           650) #total hours

sol<-lp("max", f.obj, f.con, f.dir, f.rhs, compute.sens = TRUE)
```

**The optimal solution ($): ** 
```{r echo=FALSE, message=FALSE, warning=FALSE}
sol$objval
```
To achive the optimal solution you need to make 15 `All American` and 20 `Dantzig`

```{r echo=FALSE, message=FALSE, warning=FALSE}
sol$solution
sol$duals
```

## Homework 14 part 2

Memoryless bar, on the other hand, is tired of running out of inventory and missing a lot of potential sales. They have hired you to help them figure out what they need to do to have a probability of 60% or higher of having 2 kegs on hand in the long run. There are several things that you can change to attempt this task: changing the order rules, expanding the chain to allow for more inventory to accumulate. Experiment with a few of these and make a recommendation to the bar owners, your recommendation should include a diagram, a transition matrix, and the steady-state values.
```{r}

```



